Forcing for Isabelle

### 2018-12-19 LICS/easy-axioms.tex
correcciones a primeros párrafos

Extensionality for $M[G]$ is straightforward because $M[G]$ is
transitive. %\footnote{We generalized slightly some results by Paulson:
%  in fact, several basic lemmas are valid for any transitive class
%  (for instance, absoluteness of Union). We plan to define a new
%  hierarchy of locales for ZF where transitive classes will be at the
%  base.}
In fact, for $x,y\in M[G]$, we can prove
$\forall w. w\in x \leftrightarrow w\in y$ (notice that the binding
$w$ is not relativized), because $M[G]$ is transitive; therefore by
extensionality we conclude $x=y$.

Foundation for $M[G]$ does not depend on $M[G]$ being transitive: in
this case we take $x\in M[G]$ and prove that there is an
$\in$\kern -1pt-minimal element, relativized to $M[G]$, in $x$. Using
foundation for $x\cap M[G]$ we get a minimal $y$ (which is not
relativized to $M[G]$), so it is still minimal when relativized to
$M[G]$.

>>>>

For Extensionality in $M[G]$, the assumption 
$\forall w[M[G]]. w\in x \leftrightarrow w\in y$ yields 
$\forall w. w\in x \leftrightarrow w\in y$ by transitivity of $M[G]$. %\footnote{We generalized slightly some results by Paulson:
%  in fact, several basic lemmas are valid for any transitive class
%  (for instance, absoluteness of Union). We plan to define a new
%  hierarchy of locales for ZF where transitive classes will be at the
%  base.}
Therefore, by (ambient) Extensionality we conclude $x=y$.

Foundation for $M[G]$ does not depend on $M[G]$ being transitive: in
this case we take $x\in M[G]$ and prove, relativized to $M[G]$,  that there is an
$\in$\kern -1pt-minimal element in $x$. Instantiating the global Foundation
Axiom for $x\cap M[G]$ we get a minimal $y$, so it is still minimal
when considered relative to $M[G]$.

It is noteworthy that the proofs in the Isar dialect of Isabelle
strictly follow the argumentation of the two previous paragraphs.
